MSD panels 1, 2 and 3 Explant Supernatant

### 2016-09-23 MSD_panels_1_2_3_explant_sup_analysis.Rmd
made a new logfc file with different analyte names and order

>>>>

Here is the same heat map with some changes to to Assay names and order:

```{r rename analytes logFC heatmap, echo=FALSE}

#make a new column to hold the new names
merge24And3<-merge24And3 %>%
  mutate(altAssayNames = ifelse(Assay == "MIG",
                                "CXCL9",
                                ifelse(Assay == "IP-10",
                                       "CXCL10",
                                       ifelse(Assay == "IL1-RA","IL-1RA",as.character(Assay)))))

#factor the new assay names in the order FH wanted:
#Note that the FIRST level will be at the bottom of the heat map axis!!!

merge24And3$altAssayNames<-factor(merge24And3$altAssayNames)

merge24And3$altAssayNames<-factor(merge24And3$altAssayNames, levels(merge24And3$altAssayNames)[c(3,14,7,18,16,17,8,6,5,12,19,4,20,15,13,11,9,10,1,2)])

ggplot(merge24And3, aes(x = Donor, y = altAssayNames))+
  geom_tile(aes(fill = max10fold), color = "gray")+
  scale_fill_gradient2(low = "green", mid = "white", high = "red", midpoint = 0, name = "log10 Fold Change")+
  facet_wrap(~Virus, scales = "free_x")+
  labs( y = "Assay")+
  ggtitle("log fold change of concentrations at 24hrs over 3 hrs")
